Report and Figures

### 2016-11-01 5_figs.Rmd
centered checkerboard

```{r, fig.height=3}
g <- checkerboard_illustration() 
g + theme(text=element_text(size=16, family="Palatino"))
ggsave('figs/checkerboard.pdf', width = 4, height = 1.5)
embed_fonts("figs/checkerboard.pdf", outfile="figs/checkerboard.pdf")
```

@@

```{r}
make_cluster_groups('Detroit', 6) %>% 
	mutate(race = factor(race, levels = c('Other', 'Asian', 'Hispanic', 'Black', 'White'))) %>% 
  group_by(cluster) %>% 
  mutate(alpha = p / sum(p),
         total = sum(p)) %>% 
	ggplot(aes(y = race, x = cluster, fill = cluster)) + 
  scale_fill_brewer(palette = 'Set3', name = NULL, guide = 'none', labels = LETTERS[1:nclusters]) + 
	geom_tile(color = 'black',  aes(alpha = alpha), size = 1) + 
	geom_text(aes(
		label = ifelse(p < 0.005, "", 100 * round(p,2))), size = 8, family = 'Palatino') + 
  scale_alpha_continuous(guide = 'none', limits = c(0, .3)) + 
	theme_minimal() + 
	theme(text=element_text(size=16, family="Palatino"),
		  axis.ticks.x = element_blank(),
		  axis.title = element_blank(),
		  legend.position="bottom",
		  legend.title = element_blank(),
		  line = element_blank(),
		  text = element_text(size = 25))

>>>>

```{r, fig.height=3}

checkerboard_illustration <- function(){
	expand.grid(x = 1:8, y = 1:8) %>%
		mutate(`(a)` = 1,
			   `(b)` = .5,
			   `(c)` = (x > 4)*1,
			   `(d)` = (x + y) %% 2) %>%
		gather(key = model, value = p, -x, -y) %>%
		ggplot(aes(x = x, y = y)) +
		ggthemes::theme_map() +
		theme(axis.ticks = element_blank(),
			  axis.text.x = element_blank(),
			  axis.text.y = element_blank(),
			  panel.margin = unit(1, "mm"),
			  panel.background = element_rect(),
			  panel.grid.major = element_line(size = 0),
			  panel.grid.minor = element_line(size = 0),
			  strip.background = element_rect(fill = "white", color = "white", size = 2),
			  plot.margin=unit(c(0,1,0,0),"mm")) +
		geom_tile(aes(fill = p)) +
		scale_fill_continuous(low = 'white', high = 'black ', limits=c(0,1)) +
		facet_grid(~model) +
		xlab('') +
		ylab('') +
		guides(fill=FALSE)
}

g <- checkerboard_illustration() 
# g + theme(text=element_text(size=10, family="Palatino"))
ggsave('figs/checkerboard.pdf', width = 4, height = 1.3)
embed_fonts("figs/checkerboard.pdf", outfile="figs/checkerboard.pdf")
```

@@

```{r}
make_cluster_groups('Detroit', 6) %>% 
	mutate(race = factor(race, levels = c('Other', 'Asian', 'Hispanic', 'Black', 'White'))) %>% 
  group_by(cluster) %>% 
  mutate(alpha = p / sum(p),
         total = sum(p)) %>% 
	ggplot(aes(y = race, x = cluster, fill = cluster)) + 
  scale_fill_brewer(palette = 'Set3', name = NULL, guide = 'none', labels = LETTERS[1:nclusters]) + 
	geom_tile(color = 'black',  aes(alpha = alpha), size = 1) + 
	geom_text(aes(
		label = ifelse(p < 0.005, "", 100 * round(p,2))), size = 8, family = 'Palatino') + 
  scale_alpha_continuous(guide = 'none', limits = c(0, .3)) + 
	theme_minimal() + 
	theme(text=element_text(size=25, family="Palatino"),
		  axis.ticks.x = element_blank(),
		  axis.title = element_blank(),
		  legend.position="bottom",
		  legend.title = element_blank(),
		  line = element_blank())
